RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-02-26 main.tex
:triangular_flag_on_post: Geoffrey 230226

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with common amplitude scattering ratio $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
	We choose $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{e3} channel realizations.

@@

			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}

@@

			\item \emph{\gls{ris}:} Since the backscatter symbol tuple $x_{\mathcal{K}}$ is deterministic, the total backscatter rate is zero and the primary achievable rate becomes a special case of \eqref{eq:primary_mutual_information}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		% However, the primary rate benefit
		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} (especially at low \gls{snr}).
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \gls{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Since problem \eqref{op:input_distribution} is convex when $K=1$, the \gls{kkt} solution is always global optimal in this case.} at different primary \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is zero on two states and nearly uniform on the other two.
		This is because, due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as illustrated in Fig.~\ref{fg:energy_distribution}.
		In such cases, the extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middle ones may not provide enough energy difference and thus end up unused.
		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming, which suggests RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
				\resizebox{0.6\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.
			}
		\end{figure}
		\begin{subsubsection}{Input Distribution}
			We compare these input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} result evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
			\end{itemize}
			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
				% guided by correlation matrix \cite{Calvo2010}.
			\end{itemize}

			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
			We observe \emph{Cooperation} provides the outer bound since joint encoding is always beneficial.
			The \emph{average} rate performance of \emph{Exhaustion} and \emph{\gls{kkt}} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
			\emph{Equiprobable} experiences minor backscatter and major primary rate losses without \gls{csi}- and \gls{qos}-adaptive backscatter encoding.
			Both gaps should become larger when $M$ and $K$ increase.
			For the recovery methods, the simple \emph{Marginalization} provides a close result to \emph{\gls{kkt}}, but \emph{Randomization} and \emph{Decomposition} fail our expectations for most channel realizations.
			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantages of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}

@@

			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
			In the low-$\rho$ regime, the proposed \emph{\gls{pgd}} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
			This is because backscatter detection relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
			Such an energy diversity is enhanced by \emph{\gls{pgd}} that effectively exploits backscatter constellation and input distribution knowledge, rather than simply maximizing the direct/ergodic equivalent \gls{snr}.
			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \emph{\gls{pgd}} beamformer becomes closer to both \gls{mrt} schemes.
			At $\rho=1$, \emph{\gls{pgd}} and \emph{E-\gls{mrt}} boil down to \gls{mrt} towards the deterministic composite channel as in \gls{ris} literature \cite{Wu2019}.
			Besides, the difference between \emph{E-\gls{mrt}} and \emph{D-\gls{mrt}} can be insignificant for dispersed RIScatter nodes.
			Those observations prove the proposed \emph{\gls{pgd}} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region for RIScatter.
		\end{subsubsection}

@@

			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
			The distribution-aware schemes \emph{\gls{dp}}, \emph{\gls{smawk}} and \emph{Bisection} ensure higher total backscatter rate than the non-adaptive \emph{\gls{ml}}.
			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection chances of other hypotheses.
			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
		\end{subsubsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fg:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a classic passive array gain of $N^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more transmitter-scatter-receiver paths become available to \emph{\gls{pgd}} and their diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which leads to a larger achievable rate region.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
		\end{subsubsection}

		\begin{subsubsection}{Spreading factor}
			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region, where the unit of total backscatter rate is bits per primary block (to indicate throughput).
			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection can thus be unreliable.
			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$, although nodes are encoding at higher gross rate.
			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should account for multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
		\end{subsubsection}

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better detection performance.
		\end{subsubsection}

		\begin{subsubsection}{Coverage Disk Radius}
			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
			We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
			This is because the double fading effect is less severe for near-far setups.
			In a multi-user RIScatter system with dispersed nodes, each node may be allocated to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
	\label{st:simulation_results}
\end{section}

>>>>

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
	We choose $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{e3} channel realizations.

@@

			The primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we regard the scattered component $\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]$ as \gls{awgn} during primary decoding \cite{Long2020a}.}

@@

			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		% However, the primary rate benefit
		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \gls{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
				\resizebox{0.6\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.
			}
		\end{figure}
		\begin{subsubsection}{Input Distribution}
			We compare these input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
			\end{itemize}
			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
				% guided by correlation matrix \cite{Calvo2010}.
			\end{itemize}

			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
			We observe Cooperation provides the outer bound since joint encoding is always beneficial.
			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as stated in Remark \ref{re:input_kkt_distribution}.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
			Both rate gaps should be larger when $M$ and/or $K$ increase.
			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}

@@

			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
			In the low-$\rho$ regime, the proposed \gls{pgd} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
			This is because the semi-coherent backscatter decoding relies on the \emph{relative difference} of accumulated energy under different symbol tuples.
			Such an energy diversity is enhanced by \gls{pgd} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizing the direct/ergodic \gls{snr}.
			As $\rho$ increases, the primary equivalent \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit} and \gls{pgd} beamformer becomes closer to both \gls{mrt} schemes.
			At $\rho=1$, both \gls{pgd} and E-\gls{mrt} boil down to \gls{mrt} towards the composite channel.
			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
			Those observations prove the proposed \gls{pgd} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to balance the primary equivalent \gls{snr} and backscatter energy difference and enlarge the achievable rate region.
		\end{subsubsection}

@@

			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal threshold design heavily depends on input distribution.
			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions in order to increase the success detection rates of other hypotheses.
			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
		\end{subsubsection}

@@

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_tags.tex}
				}
			}
			\subfloat[Input States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_noise.tex}
				}
			}
			\subfloat[Disk Radius\label{fg:region_coverage}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_coverage.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$ as a reference.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influence the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary equivalent \gls{snr} but also influences the relative energy difference that other nodes can create.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a conventional passive array gain $N^2$.
		\end{subsubsection}

@@

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more scattered paths are available to \gls{pgd} and the channel diversity can be further exploited to enhance the primary equivalent \gls{snr} and backscatter energy difference, which enlarges the achievable rate region.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pgd} design.
		\end{subsubsection}

		\begin{subsubsection}{Spreading factor}
			Fig.~\subref*{fg:region_duration} presents how the spreading factor $N$ affects the achievable rate region.
			Please notice here the unit of total backscatter rate is bits per primary block to indicate throughput.
			Apparently, using a very large $N$ can severely constrain the backscatter throughput, since the gain in energy certainty (by law of large numbers) cannot withstand the loss in gross rate.
			As $N \to \infty$, RIScatter nodes boil down to \gls{ris} elements with fixed reflection pattern during whole channel block and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the equivalent \gls{dmmac} \eqref{eq:dmmac} has very high error probabilities and the energy detection is thus unreliable.
			It explains the observation that $N=10$ provides lower backscatter achievable rate than $N=20$.
			Therefore, we conclude the design of spreading factor $N$ in RIScatter systems should accommodate multiple factors (e.g., data rate requirements, load switching constraints at the nodes, and signal processing capability at the user).
		\end{subsubsection}

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better energy detection performance.
		\end{subsubsection}

		\begin{subsubsection}{Coverage Disk Radius}
			Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
			We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
			This is because the double fading effect is less severe for near-far setups.
			In a multi-user RIScatter system with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
	\label{st:simulation_results}
\end{section}

\begin{section}{Conclusion}
	This paper introduced RIScatter as a low-power scatter protocol that simultaneously enables backscatter modulation and dynamic passive beamforming by smart input distribution design.
	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris} as special cases, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
	We also propose a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to guarantee primary benefit and improve backscatter throughput.
	The achievable primary-total-backscatter rate region is then studied for a single-user multi-node RIScatter system, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
	Numerical results not only validated the proposed algorithms but also emphasized the importance of adaptive input distribution and cooperative decoding for both primary and backscatter links.

	One possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
	Another interesting question is how to design RIScatter node and receiver in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
	% If one node can be decoded by multiple users, its input distribution may be further adjusted to mimic the multi-beam gain of dynamic passive beamforming \cite{Qiu2022}.
	% This will be answered in our future work.
\end{section}
